Embracing the Laws of Physics: \\ Three Reversible Models of Computation

### 2018-06-11 survey/survey.tex
cite mfps

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data II: Structured Finite Types}

@@

%%%
\section{Data III: Reversible Programs between Reversible Programs}

\begin{verbatim}
Mention convention:

level 0: types
level 1: type equivalences (pi combinators)
level 2: equivalences between equivalences

(cite MFPS invited paper)
\end{verbatim}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data II: Structured Finite Types}
\label{sec:pi1}

@@

%%%
\section{Data III: Reversible Programs between Reversible Programs}
\label{sec:pi2}

@@

Our reversible language of type isomorphisms and equivalences between
them has a strong connection to \emph{univalent universes} in
HoTT~\cite{CARETTE20185}. Based on this connection, we refer to the
types as being at level-0, to the equivalences between types (i.e., the
combinators of Sec.~\ref{sec:pi1}) as being at level-1, and to the
equivalences between equivalences of types (i.e., the combinators
discussed in this section) as being at level-2.
